%
% File naaclhlt2015.tex
%

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2015}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{url}
\setlength\titlebox{6.5cm}    % Expanding the titlebox
\bibliographystyle{plain}

\title{Minerva \\ Question-answering system}

\author{Meris Bahtijaragic\\
	    {\tt dat11mba@student.lu.se}
	    \And
      \\
      \\
      \\
      \textbf{Tim Dolck}\\
      {\tt dat11tdo@student.lu.se}
      \And
      Julian Kron\'{e}\\
      {\tt dat11jkr@student.lu.se}
}

\date{}

\begin{document}
\maketitle
\begin{abstract}
\input{sections/abstract.tex}
\end{abstract}
\section{Introduction}
\input{sections/introduction.tex}
\section{Passage Retrieval}
\input{sections/passage_retrieval.tex}
\section{Question Processing}
\input{sections/question_processing.tex}
\section{Answer Extraction}
\input{sections/answer_extraction.tex}
\section{Results and evaluation}
\input{sections/results_and_evaluation.tex}
\section{Conclusion}
\input{sections/conclusion.tex}

\begin{thebibliography}{}

\iffalse
\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.
\fi

\bibitem[\protect\citename{Juri Pyykk\"o, Rebecka Weegar, Piere Nugues}2014]{QASYS}
Juri Pyykk\"o, Rebecka Weegar, Pierre Nugues.
\newblock 2014.
\newblock Passage Retrieval in a Question Answering System. 
\newblock Proceedings of the Fifth Swedish Language Technology Conference, Uppsala, 2014.
\newblock \url{http://www2.lingfil.uu.se/SLTC2014/abstracts/sltc2014_submission_3.pdf}

\bibitem[\protect\citename{Robert \"Ostling}2013]{stagger}
Robert \"Ostling.
\newblock 2013.
\newblock {\em Stagger: an Open-Source Part of Speech tagger for Swedish}.
\newblock Northern European Journal of Language Technology, 2013.
\newblock \url{http://www.ling.su.se/polopoly_fs/1.151578.1381924405!/menu/standard/file/nejlt13v3a1.pdf}

\bibitem[\protect\citename{The Apache Software Foundation}2015]{lucenecore}
The Apache Software Foundation \\
\newblock Apache Lucene Core \\
\newblock \url{http://lucene.apache.org/core/} \\
\newblock 2015-01-03

\bibitem[\protect\citename{The Wikimedia Foudation}2015]{wikimedia}
The Wikimedia Foundation \\
\newblock Wikimedia Downloads \\
\newblock \url{http://dumps.wikimedia.org/} \\
\newblock 2015-01-03

\bibitem[\protect\citename{Giuseppe Attardi, Antonio Fuschetto}2013]{wikiextractor}
Guiseppe Attardi, Antonio Fuschetto. \\
\newblock 2013
\newblock Wikipedia Extractor \\
\newblock \url{http://medialab.di.unipi.it/wiki/Wikipedia_Extractor} \\

\bibitem[\protect\citename{Athens University of Economics and Business}2015]{bm25similarity}
Athens University of Economics and Business \\
\newblock The BM25 similarity function \\
\newblock \url{http://ipl.cs.aueb.gr/stougiannis/bm25.html} \\
\newblock 2015-01-03

\bibitem[\protect\citename{The Apache Software Foundation}2015]{tfidfsimilarity}
The Apache Software Foundation \\
\newblock Class TFIDFSimilarity \\
\newblock \url{https://lucene.apache.org/core/4_0_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html} \\
\newblock 2015-01-03

\bibitem[\protect\citename{Chih-Jen Lin et al.}2014]{liblinear}
Chih-Jen Lin et al. \\
\newblock 2014 \\
\newblock {\em LIBLINEAR -- A Library for Large Linear Classification} \\
\newblock \url{http://www.csie.ntu.edu.tw/~cjlin/liblinear/}

\end{thebibliography}

\end{document}
